Dependent Object Types

### 2012-08-31 doc/candidacy/report.tex
reorg with examples at the end of each section

% TODO: example of translucent module and its utility. woudl be nice to re-use this example in nuObj to show how it can be encoded

@@

@@

Let's now re-use an example from the paper, and discuss how we would
emulate it in Scala.
\begin{lstlisting}
class Graph {
  class Node {
    Edge connect(Node other) {
      return new Edge(this, other);
    }
  }
  class Edge {
    Node from, to;
    Edge(Node f, Node t) { from = f; to = t; }
  }
}

@@

Let's now illustrate with a few examples the correspondences outlined
earlier.

First, we show how to encode monomorphic functions into the
calculus. The paper goes further and generalizes the encoding to
system $F_{<:}$. A $\lambda$-abstraction $\lambda ( x : T )\; t$ is
represented as a class with an abstract member \code!arg! for the
function argument:
\begin{lstlisting}
[x: {arg: T}| fun = [res = $t'$]]
\end{lstlisting}
$t'$ corresponds to term $t$ in which all occurrences of $x$ are
replaced by \code!$x$.arg!. We cannot directly access \code!arg! on
the right-hand side of \code!fun!: this wouldn't be ``contractive'',
because \code!arg! might not be initialised before \code!fun!. Hence,
we pack $t'$ in another class to ensure contractiveness. Now, an
application $g(e)$ gets decomposed into three subsequent steps:
\begin{lstlisting}
$\nu\,$g$_{app}$  <- g & [arg = e];
$\nu\,$g$_{eval}$ <- g$_{app}$.fun;
g$_{eval}$.res
\end{lstlisting}
First we instantiate function \code!g! with a concrete argument
yielding a thunk \code!g$_{app}$!. Then we evaluate this thunk by
creating an instance \code!g$_{eval}$! of it. Finally we extract the
result by querying field \code!res! of \code!g$_{eval}$!.

% TODO: example of module encoding... perhaps in Scala rather than nuObj?

@@

>>>>

@@

\subsubsection*{SML Example and Scala Encoding}
TODO

@@

\subsubsection*{Tribe Example and Scala Encoding}
Let's now re-use an example from the paper, and discuss how we would
emulate it in Scala.
\begin{lstlisting}
class Graph {
  class Node {
    Edge connect(Node other) {
      return new Edge(this, other);
    }
  }
  class Edge {
    Node from, to;
    Edge(Node f, Node t) { from = f; to = t; }
  }
}

@@

@@

\subsubsection*{${\nu}Obj$ Example}

We show how to encode monomorphic functions into the
calculus. The paper goes further and generalizes the encoding to
system $F_{<:}$.

A $\lambda$-abstraction $\lambda ( x : T )\; t$ is represented as a
class with an abstract member \code!arg! for the function argument:
\begin{lstlisting}
[x: {arg: T}| fun = [res = $t'$]]
\end{lstlisting}
$t'$ corresponds to term $t$ in which all occurrences of $x$ are
replaced by \code!$x$.arg!. We cannot directly access \code!arg! on
the right-hand side of \code!fun!: this wouldn't be ``contractive'',
because \code!arg! might not be initialised before \code!fun!. Hence,
we pack $t'$ in another class to ensure contractiveness. Now, an
application $g(e)$ gets decomposed into three subsequent steps:
\begin{lstlisting}
$\nu\,$g$_{app}$  <- g & [arg = e];
$\nu\,$g$_{eval}$ <- g$_{app}$.fun;
g$_{eval}$.res
\end{lstlisting}
First we instantiate function \code!g! with a concrete argument
yielding a thunk \code!g$_{app}$!. Then we evaluate this thunk by
creating an instance \code!g$_{eval}$! of it. Finally we extract the
result by querying field \code!res! of \code!g$_{eval}$!.

This example illustrates the correspondence between classes, methods
and functors claimed by ${\nu}Obj$.
